---
title: "Volatility Forecasting"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 

```



# **Convert data into _time series_**

```{r 1, include=TRUE}
#################################  Convert data into time series  ####################################################################### 
setwd("C:/Users/ddaya/OneDrive/Data Science Portfolio/Quantitative Finance")
# import dataset
library(zoo)
StockData <- read.zoo("GOOG.csv",header = TRUE, sep = ",",format="%Y-%m-%d")
PriceData<-ts(StockData$Adj.Close, frequency = 5) # Frequency=5 because it is set on only business days

# Note:
#Frequency = 12 means that data is at monthly level
# Frequency = 4 means that data is at quarterly level
# Frequency = 6 means data points for every 10 minutes of an hour
# Frequency = 5 means that data is at daily level business day

plot(StockData$Adj.Close,type="l") # plots stock movement through time

```


*log the difference of the variable to get the percentage change*
```{r 2, include=TRUE}

# log and difference the variable
GOOGLE_Price<-log(diff(StockData$Adj.Close))
 library(zoo)
    GOOGLE_Price <- na.locf(GOOGLE_Price) # to handle NA values (from weekends and holidays)
plot(GOOGLE_Price, ylab="",xlab="") 
abline(h=0, col="dark grey", lty=3, lwd=3)


```


**Key Takeaway*: For the most part, GOOGLE stock performs at +2% -- +4% above average whenever the market has a positive shock. Similarly, it almost always performs above average, at about +1.5% -- +2%. Additionally, it has some very bad negative performance, at around -3% -- -4% when the market suffers a negative shock, but it immediately recuperates (by performing above average) the next day. 

**Diagnostics**
```{r 3, include=TRUE}
acf(GOOGLE_Price, na.action=na.pass)

```
```{r 4, include=TRUE}
pacf(GOOGLE_Price, na.action=na.pass)
```

**Note**: Our *ACF* portrays a non-stationary process. For an AR(p) model we need and ACF plot that decays slowly, and a PACF plot that cuts off after x lags; which would then lead us to conclude that the order of AR(p=x). We do not have any of those conditions, so we can’t operate
an AR(p) model.

Our ACF decays slowly and ends at 3. Similarly, our PACF decays suddenly after the first spike, so it could be ARIMA(3,1,0) 


# ARIMA Model
```{r 5, include=TRUE}
ar3<-arima(GOOGLE_Price, c(3,1,0))
ar3

```
# GARCH Model

```{r pressure, echo=FALSE}
library(rugarch)

GARCH_Model<-ugarchspec(mean.model = list(armaOrder = c(3,0)),variance.model = list(garchOrder = c(1,1), model = "sGARCH"), distribution.model = "norm")

GARCH_Model
```
```{r 7, include=TRUE}
GARCH_Fit<-ugarchfit(GARCH_Model, data=GOOGLE_Price)
GARCH_Fit
```
  

__Notice__:

Based on the output, the estimated mean of the series is $\mu$=3.73786, and the estimated variance is $\omega+\alpha_1+\beta_1$=0.07028+0.07264+0.06565=0.20857


# Variance volatility series
```{r 8, include=TRUE}
# convert the fitted values into time series
library(readr)
    StockData <- read_csv("GOOG.csv")
      library(zoo)
          dt = as.Date(StockData$Date, format="%Y-%m-%d")
            Stockdataz = zoo(x=GARCH_Fit@fit$sigma^2, order.by=dt) 
```

```{r 8.2, include=TRUE} 
# view the first values of our new time series
              head(Stockdataz)
```

```{r 9, include=TRUE}
# view the last values of our new time series
tail(Stockdataz)
```

**Visualize our model**
```{r 10, include=TRUE}
plot(Stockdataz, xlab="", ylab="", main=" GOOGLE Volatility - GARCH(1,1)")
```

# Forecast
We will forecast the percentage change in GOOGLE stock for January
```{r 11, include=TRUE}
FutureForecast=ugarchforecast(GARCH_Fit, n.ahead = 20)
FutureForecast
```


```{r 12, include=TRUE}
     'Stock Price'<-as.data.frame(FutureForecast@forecast)
            `Stock Price`<-`Stock Price`$X2020.12.29.1
              plot(`Stock Price`, col='red', type='l')
                title("GOOGLE January Forecast")
            
```





Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
