---
title: "Prediction Evaluation"
author: "Dayanara M."
date: "February 4, 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```



# **Step 1: Import models**
```{r 1, include=TRUE}
###################################### set working directory ##########################################
setwd("C:/Users/ddaya/OneDrive/Data Science Portfolio/Quantitative Finance")

#################################### Step 1: Import models ###########################################

# Run our ARMA and GARCH models
load("ARIMA_models.RData")
load("GARCH_models.RData")
```


# **Step 2: K-fold Cross Validation**
 This is a regular k-fold cross-validation for autoregressive models. Although cross-validation is sometimes not valid for time series models, it does work for autoregressions. Theory on the appropriateness of K-Fold cross validation for time series can be seen [here](https://robjhyndman.com/publications/cv-time-series/). 
         

```{r 2, include=TRUE}

################################### Step 2: K-fold Cross Validation ##################################


library(forecast)
modelcv_Arima <- CVar(PriceArima$fitted, k=5)                    # ARIMA
  CV_Arima<-as.data.frame(modelcv_Arima$CVsummary)
    colnames(CV_Arima)<- c("Arima_Mean", "Arima_SD")
modelcv_Arch <- CVar(arch.fit@fit[["fitted.values"]], k=5)       # ARCH
  CV_Arch<-as.data.frame(modelcv_Arch$CVsummary)
    colnames(CV_Arch)<- c("Arch_Mean", "Arch_SD")
modelcv_Garch<- CVar(gfit.ru@fit[["fitted.values"]], k=5)        # GARCH 
  CV_Garch<-as.data.frame(modelcv_Garch$CVsummary)
    colnames(CV_Garch)<- c("Garch_Mean", "Garch_SD")
modelcv_EGarch<- CVar(egarchsnp.fit@fit[["fitted.values"]], k=5) # EGARCH
  CV_EGarch<-as.data.frame(modelcv_EGarch$CVsummary)
    colnames(CV_EGarch)<- c("Garch_Mean", "Garch_SD")
    
# for the multivariate GARCH, I will only choose the GOOGLE stats
  H<-as.data.frame(dcc_fit@model[["mu"]])
    H1<-H[,1]
modelcv_VGarch<- CVar(H1, k=5)                                   # VGARCH
  CV_VGarch<-as.data.frame(modelcv_VGarch$CVsummary)
    colnames(CV_VGarch)<- c("VGarch_Mean", "VGarch_SD")
    
# for the DCC, I will only choose the GOOGLE stats
  H<-as.data.frame(dcc_fit_2@model[["mu"]])
    H2<-H[,1]
modelcv_DCC<- CVar(H1, k=5)
  CV_DCC<-as.data.frame(modelcv_DCC$CVsummary)                   # DCC
    colnames(CV_DCC)<- c("DCC_Mean", "DCC_SD")
    
# merge all k - folds
    # merge multiple datasets
 K_Folds <- Reduce(function(x, y) merge(x, y, all=TRUE), 
                   list(CV_Arima, CV_Arch, CV_Garch,
                        CV_EGarch, CV_VGarch, CV_DCC))
# data frame of all K-Folds
K_Folds<-cbind(CV_Arima, CV_Arch, CV_Garch,
               CV_EGarch, CV_VGarch, CV_DCC)

names(K_Folds)[7]<-"Egarch_Mean"
names(K_Folds)[8]<-"Egarch_SD"

```


**Cross Validation Results**
```{r 16666, include=TRUE}
K_Folds[,1:5]
```
```{r 166661, include=TRUE}
K_Folds[,6:11]
```

```{r 166662, include=TRUE}
K_Folds[,11:12]
```


**Selecting the best model**
```{r 16548, include=TRUE}
# Retrive the best models, by each estimators account
  A1<-rownames(K_Folds)[1] # retrieves the statistic
      DF<-as.table(which(K_Folds==min(K_Folds[1,]), arr.ind=TRUE))
        B1<-colnames(K_Folds)[DF[,2]] 
   
        
  A2<-rownames(K_Folds)[2] # retrieves the statistic
    DF<-as.table(which(K_Folds==min(K_Folds[2,]), arr.ind=TRUE))
      B2<-as.matrix(colnames(K_Folds)[DF[,2]])
        B2<-B2[1,]
        
        
  A3<-rownames(K_Folds)[3] # retrieves the statistic
    DF<-as.table(which(K_Folds==min(K_Folds[3,]), arr.ind=TRUE))
      B3<-as.matrix(colnames(K_Folds)[DF[,2]])
        B3<-B3[1,]
        
        
        
  A4<-rownames(K_Folds)[4] # retrieves the statistic
    DF<-as.table(which(K_Folds==min(K_Folds[4,]), arr.ind=TRUE))
      B4<-colnames(K_Folds)[DF[,2]] 
      
      
  A5<-rownames(K_Folds)[5] # retrieves the statistic
    DF<-as.table(which(K_Folds==min(K_Folds[5,]), arr.ind=TRUE))
      B5<-colnames(K_Folds)[DF[,2]] 
      
      
  A6<-rownames(K_Folds)[6] # retrieves the statistic
    DF<-as.table(which(K_Folds==min(K_Folds[6,1:10]), arr.ind=TRUE))
      B6<-colnames(K_Folds)[DF[,2]] 
      
      
  A7<-rownames(K_Folds)[7] # retrieves the statistic
    DF<-as.table(which(K_Folds==min(K_Folds[7,1:10]), arr.ind=TRUE))
      B7<-colnames(K_Folds)[DF[,2]] 
   
      
# Generate data frame with results
      Estimator<-c(A1,A2,A3,A4,A5,A6,A7)
        Model<- c(B1,B2,B3,B4,B5,B6,B7)
          CV_Results<-cbind(Estimator,Model)
# Verify the model that repeats itself the most over the best estimators          
      mytab<-as.table(CV_Results)
        Freq_Table<-ftable(mytab[,2])
            Freq_Table<-as.data.frame(Freq_Table)
              Freq_Table
```


```{r 3, include=TRUE}
        # Return the name of the model with the highest frequency      
              DF<-as.table(which(Freq_Table==max(Freq_Table[,2]), arr.ind=TRUE))
                 Freq_Table[DF[1,1],1]
```                    
                  

__CONCLUSION:__ ARCH is the best model to forecast variance, ARIMA is the best for mean point forecast, which is what we are interested in.                  
                  
                  
# **Step 3: Graph and Average Error**                  
```{r 4, include=TRUE}                  
################################### Step 3: Graph and Average Error ##################################
                

### ARIMA                
                 # convert into time series
                 library(zoo)
                 GOOG<- fortify.zoo(StockData$Adj.Close)
                 GOOG$`StockData$Adj.Close`<-as.numeric(as.character(GOOG$`StockData$Adj.Close`))
                 GOOG$Fit<-PriceArima$fitted
                 GOOG$Error <- GOOG$`StockData$Adj.Close`-GOOG$Fit
                 GOOG<-read.zoo(GOOG, tz="as.POSIXct")
                 mean(GOOG$Error) # mean error =  0.02955047
                
                 
                 plot.zoo(GOOG$`StockData$Adj.Close`, gg=TRUE, ylab='Price', col=4, type='l')  
                 lines(GOOG$Fit, col="red") 
                 title("ARIMA Model | Mean Error = 0.0296" )
                 legend("topleft", inset=c(0,0), y.intersp = 1, 
                        legend = c("Google Stock", "Fitted"),  lty = 1, bty = "n", col = c(1,2), cex = .5)
                 
                 
           
                 
### ARCH               
                 # convert into time series
                 
                 GOOG<- fortify.zoo(StockData$Adj.Close)
                 GOOG$`StockData$Adj.Close`<-as.numeric(as.character(GOOG$`StockData$Adj.Close`))
                 GOOG$Fit<-arch.fit@fit[["fitted.values"]]
                 GOOG$Error <- GOOG$`StockData$Adj.Close`-GOOG$Fit
                 GOOG<-read.zoo(GOOG, tz="as.POSIXct")
                 mean(GOOG$Error) # mean error = 0.4906739
                 
                 
                 plot.zoo(GOOG$`StockData$Adj.Close`, gg=TRUE, ylab='Price', col=4, type='l')  
                  lines(GOOG$Fit, col="red") 
                    title("ARCH Model | Mean Error = 0.4906739" )
                      legend("topleft", inset=c(0,0), y.intersp = 1, 
                        legend = c("Google Stock", "Fitted"),  lty = 1, bty = "n", col = c(1,2), cex = .5)
                
                     


                      
### GARCH                      
                      # convert into time series
                      
                      GOOG<- fortify.zoo(StockData$Adj.Close)
                      GOOG$`StockData$Adj.Close`<-as.numeric(as.character(GOOG$`StockData$Adj.Close`))
                      GOOG$Fit<-gfit.ru@fit[["fitted.values"]]
                      GOOG$Error <- GOOG$`StockData$Adj.Close`-GOOG$Fit
                      GOOG<-read.zoo(GOOG, tz="as.POSIXct")
                      mean(GOOG$Error) # mean error = -0.4768176
                      
                      
                      plot.zoo(GOOG$`StockData$Adj.Close`, gg=TRUE, ylab='Price', col=4, type='l')  
                      lines(GOOG$Fit, col="red") 
                      title("GARCH Model | Mean Error = -0.4768" )
                      legend("topleft", inset=c(0,0), y.intersp = 1, 
                             legend = c("Google Stock", "Fitted"),  lty = 1, bty = "n", col = c(1,2), cex = .5)
                     
                      
                      
                      
### EGARCH                     
                      # convert into time series
                      
                      GOOG<- fortify.zoo(StockData$Adj.Close)
                      GOOG$`StockData$Adj.Close`<-as.numeric(as.character(GOOG$`StockData$Adj.Close`))
                      GOOG$Fit<-egarchsnp.fit@fit[["fitted.values"]]
                      GOOG$Error <- GOOG$`StockData$Adj.Close`-GOOG$Fit
                      GOOG<-read.zoo(GOOG, tz="as.POSIXct")
                      mean(GOOG$Error) # mean error = -0.4848975
                      
                      
                      plot.zoo(GOOG$`StockData$Adj.Close`, gg=TRUE, ylab='Price', col=4, type='l')  
                      lines(GOOG$Fit, col="red") 
                      title("EGARCH Model | Mean Error = -0.4848975" )
                      legend("topleft", inset=c(0,0), y.intersp = 1, 
                             legend = c("Google Stock", "Fitted"),  lty = 1, bty = "n", col = c(1,2), cex = .5)
                      
                      
                      
                      
### VGARCH
                      
                      # convert into time series
                      
                      GOOG<- fortify.zoo(PriceAll)
                      GOOG$GOOGLE<-as.numeric(as.character(GOOG$GOOGLE))
                      GOOG$SP500<-as.numeric(as.character(GOOG$SP500))
                      GOOG$Fit<-H1
                      GOOG$Error <- GOOG$GOOGLE-GOOG$Fit
                      mean(GOOG$Error) # mean error = 0.354582
                      GOOG<-read.zoo(GOOG, tz="as.POSIXct")
                      
                      plot.zoo(GOOG$GOOGLE, gg=TRUE, ylab='Price', col=4, type='l')  
                      lines(GOOG$Fit, col="red") 
                      title("VGARCH Model | Mean Error = 0.3546" )
                      legend("topleft", inset=c(0,0), y.intersp = 1, 
                             legend = c("Google Stock", "Fitted"),  lty = 1, bty = "n", col = c(1,2), cex = .5)
                      
                      
                      
                      
                      
### DCC
                      
                      # convert into time series
                      
                      GOOG<- fortify.zoo(PriceAll)
                      GOOG$GOOGLE<-as.numeric(as.character(GOOG$GOOGLE))
                      GOOG$SP500<-as.numeric(as.character(GOOG$SP500))
                      GOOG$Fit<-H2
                      GOOG$Error <- GOOG$GOOGLE-GOOG$Fit
                      mean(GOOG$Error) # mean error = 0.3543684
                      GOOG<-read.zoo(GOOG, tz="as.POSIXct")
                      
                      plot.zoo(GOOG$GOOGLE, gg=TRUE, ylab='Price', col=4, type='l')  
                      lines(GOOG$Fit, col="red") 
                      title("DCC Model | Mean Error = 0.3544" )
                      legend("topleft", inset=c(0,0), y.intersp = 1, 
                             legend = c("Google Stock", "Fitted"),  lty = 1, bty = "n", col = c(1,2), cex = .5)
```                      
                 
                 
__CONCLUSION__: ARIMA has the best model fit.
                                       

#**Step 4: in-sample Backtest (1 month forward)**
```{r 6, include=TRUE}                 
################################### Step 4: in-sample Backtest (1 month forward) ##################################
   
                  
     # import data, updated from January
     library(zoo)
       Backtest_GOOG <- read.zoo("Backtest_GOOG.csv",header = TRUE, sep = ",",format="%Y-%m-%d")
   
       
       
       
  #################   ARIMA  ##############################       
    # forecast to January     
      library(forecast)                
          FutureForecast<-forecast(PriceArima,h=20) # 1 month forecast
          FutureForecast_F<-as.data.frame(FutureForecast)
          FutureForecast_F$`Point Forecast`
          # convert into time series
          GOOG<- fortify.zoo(Backtest_GOOG$Adj.Close)
          GOOG$`Backtest_GOOG$Adj.Close`<-as.numeric(as.character(GOOG$`Backtest_GOOG$Adj.Close`))
            GOOG$Forecast<-FutureForecast_F$`Point Forecast`
              GOOG$Error <- GOOG$`Backtest_GOOG$Adj.Close`-GOOG$Forecast
              mean(GOOG$Error) # mean error =  25.93711
                GOOG<-read.zoo(GOOG, tz="as.POSIXct")
          
                  
    # Graph actual vs. forecast 
          plot.zoo(GOOG$`Backtest_GOOG$Adj.Close`, gg=TRUE, ylab='Price', col=4, type='l')  
          lines(GOOG$Forecast, col="red") 
          title("ARIMA Model | Mean Error = 25.93711" )
          legend("topleft", inset=c(0,0), y.intersp = 1, 
                 legend = c("Google Stock", "Forecast"),  lty = 1, bty = "n", col = c(1,2), cex = .5)
          
    
          
          
      #################   ARCH  ##############################       
          # forecast to January  
          library(rmgarch)
          FutureForecast=ugarchforecast(arch.fit, n.ahead = 20)
          Future_For<-as.data.frame(FutureForecast@forecast)
          FutureForecast_F<-Future_For$X2020.12.29.1
          
          # convert into time series
          GOOG<- fortify.zoo(Backtest_GOOG$Adj.Close)
          GOOG$`Backtest_GOOG$Adj.Close`<-as.numeric(as.character(GOOG$`Backtest_GOOG$Adj.Close`))
          GOOG$Forecast<-FutureForecast_F
          GOOG$Error <- GOOG$`Backtest_GOOG$Adj.Close`-GOOG$Forecast
          mean(GOOG$Error) # mean error =  33.20978
          GOOG<-read.zoo(GOOG, tz="as.POSIXct")
          
          
          # Graph actual vs. forecast 
          plot.zoo(GOOG$`Backtest_GOOG$Adj.Close`, gg=TRUE, ylab='Price', col=4, type='l')  
          lines(GOOG$Forecast, col="red") 
          title("ARCH Model | Mean Error = 33.2098" )
          legend("topleft", inset=c(0,0), y.intersp = 1, 
                 legend = c("Google Stock", "Forecast"),  lty = 1, bty = "n", col = c(1,2), cex = .5)
          
          
          
          
          #################   GARCH  ##############################       
          # forecast to January     
          FutureForecast=ugarchforecast(gfit.ru, n.ahead = 20)
          Future_For<-as.data.frame(FutureForecast@forecast)
          FutureForecast_F<-Future_For$X2020.12.29.1
          
          
          # convert into time series
          GOOG<- fortify.zoo(Backtest_GOOG$Adj.Close)
          GOOG$`Backtest_GOOG$Adj.Close`<-as.numeric(as.character(GOOG$`Backtest_GOOG$Adj.Close`))
          GOOG$Forecast<-FutureForecast_F
          GOOG$Error <- GOOG$`Backtest_GOOG$Adj.Close`-GOOG$Forecast
          mean(GOOG$Error) # mean error =  6.506502
          GOOG<-read.zoo(GOOG, tz="as.POSIXct")
          
          
          # Graph actual vs. forecast 
          plot.zoo(GOOG$`Backtest_GOOG$Adj.Close`, gg=TRUE, ylab='Price', col=4, type='l')  
          lines(GOOG$Forecast, col="red") 
          title("GARCH Model | Mean Error = 6.506502" )
          legend("topleft", inset=c(0,0), y.intersp = 1, 
                 legend = c("Google Stock", "Forecast"),  lty = 1, bty = "n", col = c(1,2), cex = .5)   
          
          
          
          
          #################   EGARCH  ##############################       
          # forecast to January     
          FutureForecast=ugarchforecast(egarchsnp.fit, n.ahead = 20)
          Future_For<-as.data.frame(FutureForecast@forecast)
          FutureForecast_F<-Future_For$X2020.12.29.1
          
          
          # convert into time series
          GOOG<- fortify.zoo(Backtest_GOOG$Adj.Close)
          GOOG$`Backtest_GOOG$Adj.Close`<-as.numeric(as.character(GOOG$`Backtest_GOOG$Adj.Close`))
          GOOG$Forecast<-FutureForecast_F
          GOOG$Error <- GOOG$`Backtest_GOOG$Adj.Close`-GOOG$Forecast
          mean(GOOG$Error) # mean error =   6.319701
          GOOG<-read.zoo(GOOG, tz="as.POSIXct")
          
          
          # Graph actual vs. forecast 
          plot.zoo(GOOG$`Backtest_GOOG$Adj.Close`, gg=TRUE, ylab='Price', col=4, type='l')  
          lines(GOOG$Forecast, col="red") 
          title("EGARCH Model | Mean Error = 6.3197" )
          legend("topleft", inset=c(0,0), y.intersp = 1, 
                 legend = c("Google Stock", "Forecast"),  lty = 1, bty = "n", col = c(1,2), cex = .5)  
          
          
          
          
          #################   VGARCH  ############################## 
          # merge the GOOGLE stock and S&P500 index into one dataset
          
          
          
          SP <- read.zoo("Backtest_SP500.csv",header = TRUE, sep = ",",format="%Y-%m-%d") # import S&P 500 index
          Backtest_Data<-merge(fortify.zoo(Backtest_GOOG), fortify.zoo(SP$Adj.Close), all = FALSE) # merge with GOOGLE stock
          names(Backtest_Data)[6] <- "GOOGLE" # change column name
          names(Backtest_Data)[8] <- "SP500" # change other column name # get rid of all rows that have "null" 
          Backtest_Data<-read.zoo(Backtest_Data, tz="as.POSIXct")
       
          
          
          # forecast to January     
          fcst=dccforecast(dcc_fit,n.ahead=20)
          For<-as.data.frame(fcst@mforecast)
          GOOGLE_Forecast<-For$mu.1
          SP500_Forecast<-For$mu.2
          
          # convert into data frame
          GOOG<- fortify.zoo(Backtest_Data)
          
          # GOOGLE
          GOOG$GOOGLE<-as.numeric(as.character(GOOG$GOOGLE))
          GOOG$GOOGLE_Forecast<-GOOGLE_Forecast
          GOOG$GOOG_Error <- GOOG$GOOGLE-GOOG$GOOGLE_Forecast
          mean(GOOG$GOOG_Error) # Google mean error =  11.922
          
          # SP500
          GOOG$SP500<-as.numeric(as.character(GOOG$SP500))
          GOOG$SP500_Forecast<-SP500_Forecast
          GOOG$SP500_Error <- GOOG$SP500-GOOG$SP500_Forecast
          mean(GOOG$SP500_Error) # SP500 mean error =  -7.850106
          
          
          GOOG<-read.zoo(GOOG, tz="as.POSIXct")
          
          
          # Graph actual vs. forecast 
          plot.zoo(GOOG$GOOGLE, gg=TRUE, ylab='Price', col=4, type='l')  
          lines(GOOG$GOOGLE_Forecast, col="red") 
          title("VGARCH | GOOGLE Mean Error = 11.922" )
          legend("topleft", inset=c(0,0), y.intersp = 1, 
                 legend = c("GOOGLE Stock", "GOOGLE Forecast"),
                 lty = 1, bty = "n", col = c(1,2), cex = .5)  
          
          
          
          
          
          #################   DCC  ##############################       
          # forecast to January     
          fcst=dccforecast(dcc_fit_2,n.ahead=20)
          For<-as.data.frame(fcst@mforecast)
          # For
          GOOGLE_Forecast<-For$mu.1
          SP500_Forecast<-For$mu.2
          
          # convert into data frame
          GOOG<- fortify.zoo(Backtest_Data)
          
          # GOOGLE
          GOOG$GOOGLE<-as.numeric(as.character(GOOG$GOOGLE))
          GOOG$GOOGLE_Forecast<-GOOGLE_Forecast
          GOOG$GOOG_Error <- GOOG$GOOGLE-GOOG$GOOGLE_Forecast
          mean(GOOG$GOOG_Error) # Google mean error =  11.91674
          
          # SP500
          GOOG$SP500<-as.numeric(as.character(GOOG$SP500))
          GOOG$SP500_Forecast<-SP500_Forecast
          GOOG$SP500_Error <- GOOG$SP500-GOOG$SP500_Forecast
          mean(GOOG$SP500_Error) # SP500 mean error =  -7.854811
          
          
          GOOG<-read.zoo(GOOG, tz="as.POSIXct")
          
          
          # Graph actual vs. forecast 
          plot.zoo(GOOG$GOOGLE, gg=TRUE, ylab='Price', col=4, type='l')  
          lines(GOOG$GOOGLE_Forecast, col="red") 
          title("DCC | GOOGLE Mean Error = 11.91674" )
          legend("topleft", inset=c(0,0), y.intersp = 1, 
                 legend = c("GOOGLE Stock", "GOOGLE Forecast"),
                 lty = 1, bty = "n", col = c(1,2), cex = .5)  
```          
 

__CONCLUSION__: EGARCH is the best forecast model, because it scored the lowest mean error.


#**Step 5: Accuracy test**
```{r 7, include=TRUE}
################################### Step 5: Accuracy test ##################################
          
          
          # ARIMA
          ARIMA_ME<-mean(PriceArima$x-PriceArima$fitted)
          library(Metrics)
          ARIMA_RMSE<-rmse(PriceArima$x, PriceArima$fitted)
          ARIMA_MAE<-mae(PriceArima$x, PriceArima$fitted)
          ARIMA_MPE<-mean((PriceArima$x-PriceArima$fitted)/PriceArima$x)*(100/length(PriceArima$x-PriceArima$fitted))
          ARIMA_MAPE<-mape(PriceArima$x, PriceArima$fitted)
          ARIMA_MASE<-mase(PriceArima$x, PriceArima$fitted, step_size = 1)
          
          
          
          # ARCH
          
          # convert into time series
          
          GOOG<- fortify.zoo(StockData$Adj.Close)
          GOOG$`StockData$Adj.Close`<-as.numeric(as.character(GOOG$`StockData$Adj.Close`))
          GOOG$Fit<-arch.fit@fit[["fitted.values"]]
          GOOG$Error <- GOOG$`StockData$Adj.Close`-GOOG$Fit
          ARCH_ME<-mean(GOOG$Error) # mean error = 0.813864
          library(Metrics)
          ARCH_RMSE<-rmse(GOOG$`StockData$Adj.Close`, GOOG$Fit)
          ARCH_MAE<-mae(GOOG$`StockData$Adj.Close`, GOOG$Fit)
          ARCH_MPE<-mean((GOOG$`StockData$Adj.Close`- GOOG$Fit)/GOOG$`StockData$Adj.Close`)*(100/length(GOOG$Error))
          ARCH_MAPE<-mape(GOOG$`StockData$Adj.Close`, GOOG$Fit)
          ARCH_MASE<-mase(GOOG$`StockData$Adj.Close`, GOOG$Fit, step_size = 1)
          
          
          # GARCH
          
          # convert into time series
          
          GOOG<- fortify.zoo(StockData$Adj.Close)
          GOOG$`StockData$Adj.Close`<-as.numeric(as.character(GOOG$`StockData$Adj.Close`))
          GOOG$Fit<-gfit.ru@fit[["fitted.values"]]
          GOOG$Error <- GOOG$`StockData$Adj.Close`-GOOG$Fit
          GARCH_ME<-mean(GOOG$Error) # mean error =  -0.4768176
          library(Metrics)
          GARCH_RMSE<-rmse(GOOG$`StockData$Adj.Close`, GOOG$Fit)
          GARCH_MAE<-mae(GOOG$`StockData$Adj.Close`, GOOG$Fit)
          GARCH_MPE<-mean((GOOG$`StockData$Adj.Close`-GOOG$Fit)/GOOG$`StockData$Adj.Close`)*(100/length(GOOG$Error))
          GARCH_MAPE<-mape(GOOG$`StockData$Adj.Close`, GOOG$Fit)
          GARCH_MASE<-mase(GOOG$`StockData$Adj.Close`, GOOG$Fit, step_size = 1)
        
          
          
          
          # EGARCH
          
          # convert into time series
          
          GOOG<- fortify.zoo(StockData$Adj.Close)
          GOOG$`StockData$Adj.Close`<-as.numeric(as.character(GOOG$`StockData$Adj.Close`))
          GOOG$Fit<-egarchsnp.fit@fit[["fitted.values"]]
          GOOG$Error <- GOOG$`StockData$Adj.Close`-GOOG$Fit
          EGARCH_ME<-mean(GOOG$Error) # mean error =  0.80284
          library(Metrics)
          EGARCH_RMSE<-rmse(GOOG$`StockData$Adj.Close`, GOOG$Fit)
          EGARCH_MAE<-mae(GOOG$`StockData$Adj.Close`, GOOG$Fit)
          EGARCH_MPE<-mean((GOOG$`StockData$Adj.Close`-GOOG$Fit)/GOOG$`StockData$Adj.Close`)*(100/length(GOOG$Error))
          EGARCH_MAPE<-mape(GOOG$`StockData$Adj.Close`, GOOG$Fit)
          EGARCH_MASE<-mase(GOOG$`StockData$Adj.Close`, GOOG$Fit, step_size = 1)
      
          
          
          
          # VGARCH
          
          # convert into time series
          
          
          GOOG<- fortify.zoo(PriceAll)
          GOOG$GOOGLE<-as.numeric(as.character(GOOG$GOOGLE))
          GOOG$SP500<-as.numeric(as.character(GOOG$SP500))
          GOOG$Fit<-H1
          GOOG$Error <- GOOG$GOOGLE-GOOG$Fit
          VGARCH_ME<-mean(GOOG$Error) # mean error =  0.3639009
          library(Metrics)
          VGARCH_RMSE<-rmse(GOOG$GOOGLE, GOOG$Fit)
          VGARCH_MAE<-mae(GOOG$GOOGLE, GOOG$Fit)
          VGARCH_MPE<-mean((GOOG$GOOGLE-GOOG$Fit)/GOOG$GOOGLE)*(100/length(GOOG$Error))
          VGARCH_MAPE<-mape(GOOG$GOOGLE, GOOG$Fit)
          VGARCH_MASE<-mase(GOOG$GOOGLE, GOOG$Fit, step_size = 1)
          
          
         
          
          
          # DCC
          
          
          GOOG<- fortify.zoo(PriceAll)
          GOOG$GOOGLE<-as.numeric(as.character(GOOG$GOOGLE))
          GOOG$SP500<-as.numeric(as.character(GOOG$SP500))
          GOOG$Fit<-H2
          GOOG$Error <- GOOG$GOOGLE-GOOG$Fit
          DCC_ME<-mean(GOOG$Error) # mean error =  -71.65798
          library(Metrics)
          DCC_RMSE<-rmse(GOOG$GOOGLE, GOOG$Fit)
          DCC_MAE<-mae(GOOG$GOOGLE, GOOG$Fit)
          DCC_MPE<-mean((GOOG$GOOGLE-GOOG$Fit)/GOOG$GOOGLE)*(100/length(GOOG$Error))
          DCC_MAPE<-mape(GOOG$GOOGLE, GOOG$Fit)
          DCC_MASE<-mase(GOOG$GOOGLE, GOOG$Fit, step_size = 1)
          
          
          
          # Generate dataset with all of this data
          
          ME<-c(ARIMA_ME, ARCH_ME, GARCH_ME, EGARCH_ME, VGARCH_ME, DCC_ME)
          RMSE<-c(ARIMA_RMSE, ARCH_RMSE, GARCH_RMSE, EGARCH_RMSE, VGARCH_RMSE, DCC_RMSE)
          MAE<- c(ARIMA_MAE, ARCH_MAE, GARCH_MAE, EGARCH_MAE, VGARCH_MAE, DCC_MAE)
          MPE<-c(ARIMA_MPE, ARCH_MPE, GARCH_MPE, EGARCH_MPE, VGARCH_MPE, DCC_MPE)
          MAPE<-c(ARIMA_MAPE, ARCH_MAPE, GARCH_MAPE, EGARCH_MAPE, VGARCH_MAPE, DCC_MAPE)
          MASE<-c(ARIMA_MASE, ARCH_MASE, GARCH_MASE, EGARCH_MASE, VGARCH_MASE, DCC_MASE)
          Models<-c("ARIMA", "ARCH", "GARCH", "EGARCH", "VGARCH", "DCC")
          
          Evaluate<-data.frame(Models, ME, RMSE, MAE, MPE, MAPE, MASE)
          Evaluate
```          
        

```{r 9, include=TRUE}        
          Evaluate$Models <- levels(Evaluate$Models)[as.numeric(Evaluate$Models)] # to convert from factor to character variable
          
          # Return the name of the model with the best estimator
          
          DF<-as.table(which(Evaluate==min(abs(Evaluate[,2])), arr.ind=TRUE))
          ME<-Evaluate[DF[1,1],1]
          
          DF<-as.table(which(Evaluate==min(abs(Evaluate[,3])), arr.ind=TRUE))
          RMSE<-Evaluate[DF[1,1],1]
          
          DF<-as.table(which(Evaluate==min(abs(Evaluate[,4])), arr.ind=TRUE))
          MAE<-Evaluate[DF[1,1],1]
          
          DF<-as.table(which(Evaluate==min(Evaluate[,5]), arr.ind=TRUE))
          MPE<-Evaluate[DF[1,1],1]
          
          DF<-as.table(which(Evaluate==min(abs(Evaluate[,6])), arr.ind=TRUE))
          MAPE<-Evaluate[DF[1,1],1]
          
          DF<-as.table(which(Evaluate==min(abs(Evaluate[,7])), arr.ind=TRUE))
          MASE<-Evaluate[DF[1,1],1]
          
           
          # print the models that scored the lowest at each estimator
          
          cbind(ME, RMSE, MAE, MPE, MAPE, MASE)
```          
         
         
__CONCLUSION__: ARIMA is the best model 
          
          
#--------------------------------------------------------------------------------------------------------
                     
# RECAP OF CONCLUSIONS:
  + **K-Fold Cross** Validation = ARIMA
  + **In-sample Backtest (1 month forward)** = EGARCH 
  + **Accuracy estimates** = ARIMA 
 
 
# MODEL OF CHOICE: *EGARCH* 
I chose EGARCH, because it provided the best forecast for January, which was a very volatile month. This model is second bested by GARCH, followed by ARIMA.
 
